An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-08-06 poly-embed-journal/poly-embed-journal.tex
Pass over the appendix before vacation

\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
%\subsection{Embedding Ordered Partitions}
%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
%
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
%\begin{align*}
%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
%\end{align*}
%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
%
%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
%\begin{equation}\label{eq:ww-hinge}
%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
%\end{equation}
%
%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
%
%\begin{figure}[H]
%		\centering
%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
%	\label{fig:ordered-partition}
%\end{figure}

@@

\section{General characteristics of polyhedral functions}
\subsection{Definitions and preliminaries}
\begin{definition}[Closed halfspace]
	For any $w\in\reals^d, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$.
\end{definition}
\begin{definition}[Hyperplane]
	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$, and the boundary of $H^+_{(w,b)}$.
\end{definition}

\begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
\end{definition}

@@

%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.

  \jessie{TODO} \url{https://arxiv.org/abs/0805.0292} Prop 4.5?
\end{proof}

\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
  Add two facets and now it's a polytope.
}

\subsection{Phase 1: construct $\V^*$}
We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.

@@

We now introduce some of our notation.
\begin{itemize}
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$.
\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;-1], 0)}$. 
\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.

  % \item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.
\end{itemize}

\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
\end{claim}
\begin{proof}
  The result follows if we show $x \in \reals^\Y_+ \iff (x,c) \in \cap \H_\Y$ for all $c \in \reals$.

@@

\begin{claim}\label{claim:G-intersection-H}
  $G = \cap \H$.
\end{claim}
\begin{proof}
  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$ respectively, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{claim}\label{claim:G-unique-facets-Hstar}
  \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}

\begin{claim}\label{claim:HY-subset-Hstar}
  $\H_\Y \subseteq \H^*$.
\end{claim}
\begin{proof}
  If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$ and is concave.
  Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
\end{proof}

\begin{claim}\label{claim:unique-set-loss-vectors-defining-facets}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{claim}
\begin{proof}
  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}

  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Claim~\ref{claim:G-unique-facets-Hstar}.
  Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.

@@

\subsection{Projections to the positive orthant}
We now consider projections onto the positive orthant $\reals^\Y_+$.

@@

\begin{claim}\label{claim:pi-preserves-dim}
  For all $v\in\reals^\Y_+$, $\dim(\pi(F_v)) = \dim(F_v)$.
\end{claim}
\begin{proof}

  %\jessie{Think of the projection as a linear map and affine hull as a subspace.   Pick any point in relint of the facet, at the linear span, ...}
  %\jessie{$\affhull(F_v) = H_v$, $\dim(\affhull(\pi(F_v))) = \dim(\pi(\affhull(F_v)))$.   Show that when you project $H_v$, it gives you $\reals^\Y$.}

  \jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
  \jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
  As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
  We claim their projections $\{\pi(z_i)\}$ are affinely independent.
  Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
  We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.

@@

\raf{From notes 6/21/2021}
\jessie{Where we're going: (can be deleted)}
\begin{itemize}
\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
\end{itemize}

@@

%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
  For $\V' \subseteq \V$, we have
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3); need to move later as we havne't defined $L$ yet in this section.}
\end{claim}
\begin{proof}
  Would like to show
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
  Take any $x\in\reals^\Y_+$.
  \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}

  \raf{Another approach: assume $v^* \in \V^* \setminus \V'$.  Take $z = (x,g(x)) \in \relint(F_{v^*})$.  Argue that $x \not\in \cup_{v\in\V'} \pi(F_v)$.}

@@

\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
  For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
  \jessie{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
  Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
  Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
\end{proof}

\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L_+ = g$ (1-homog extension).}

For $x\in\reals^\Y_+$,
$\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\end{itemize}
\begin{claim}
  $G = \cap\H$.
\end{claim}
\begin{proof}
  Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
  Let $x \in \reals^\Y_+$.
  \begin{align*}
    (x,c) \in G
    &\iff g(x) \geq c & \text{ since $G$ is the hypograph of $g$}\\
    &\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
    &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
    & & \text{the inner product with $x$ and minimizable.} \\
    &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
    &\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
  \end{align*}
  Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.

\raf{Need to use minimizable}
Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in phase 1.

\begin{corollary}
  There is a set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}

Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$
\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
  For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
  \jessie{Will lead to rep iff $\Theta$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
  $\implies$
  The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
  Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

@@

\begin{claim}\label{claim:faces-contained-in-facets}
  If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. \jessie{Do we use this?}
\end{claim}
\begin{proof}
  Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
  Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.

  % subset of facet
  Moreover, the faces of $G$ are all convex polyhedra.
  Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
  \jessie{Gr\"unbaum Page 35, Section 3.1 statement 7}
\end{proof}

>>>>

%\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
\subsection{Embedding Ordered Partitions}
\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.

An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.

The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}

\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.

\begin{figure}[H]
		\centering
		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
	\label{fig:ordered-partition}
\end{figure}

@@

\section{General characteristics of polyhedra}
\subsection{Definitions and preliminaries}
\begin{definition}[Closed halfspace]
	For any $w\in\reals^d, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$.
\end{definition}
\begin{definition}[Hyperplane]
	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$, and the boundary of $H^+_{(w,b)}$.
\end{definition}

\begin{definition}[Polyhedron - halfspace representation]
	\btw{Def from Ziegler page 28}
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
\end{definition}

@@

%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.	
  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5?}
\end{proof}

\subsubsection{Notation}
Within this appendix, we use some self-contained notation.
First, for a fixed $g$ as above, define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.

We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace for some $v \in \V$.
Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our hypograph to the nonnegative orthant. 
Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;-1], 0)}$.

Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.

\subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.

@@

First, we observe that the region generated by the intersection of the $\H_y$ halfspaces restricts the hypograph to the nonnegative orthant.
\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
\end{claim}
\begin{proof}
  The result follows if we show $x \in \reals^\Y_+ \iff (x,c) \in \cap \H_\Y$ for all $c \in \reals$.

@@

Now, we can define $G$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
\begin{claim}\label{claim:G-intersection-H}
  $G = \cap \H$.
\end{claim}
\begin{proof}
  $(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$ respectively, so $(x,c) \in \cap \H$.
\end{proof}

@@

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet.
\end{lemma}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}

\begin{lemma}\label{lem:HY-subset-Hstar}
  $\H_\Y \subseteq \H^*$.
\end{lemma}
\begin{proof}
  If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$ and is concave.
  Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
\end{proof}

\begin{claim}\label{claim:unique-set-loss-vectors-defining-facets}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{claim}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.

@@

\subsection{Infinitely generated polyhedron}\label{appsubsec:phase2}

Suppose $L$ is a minimizable loss function.
For $x\in\reals^\Y_+$, consider $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$ polyhedral.
Throughout, suppose $g(x) = \risk{L}_+(x)$.
As before, take $G$ to be the hypograph of $g$.
We define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.  
Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
\begin{claim}
	$G = \cap\H$.
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in G
	&\iff g(x) \geq c & \text{ since $G$ is the hypograph of $g$}\\
	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
	& & \text{the inner product with $x$ and minimizable.} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
	\end{align*}
	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.

%\raf{Need to use minimizable}
Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in \S~\ref{appsubsec:phase1}.

\begin{corollary}\label{cor:finite-rep-set}
	There is a (finite) set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}

\subsection{Projecting from $G$ to $g$}
We now consider projections from $\reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.

@@

\begin{claim}\label{claim:pi-preserves-dim}
  For all $v\in\reals^\Y_+$, $\dim(\pi(F_v)) = \dim(F_v)$.
\end{claim}
\begin{proof}
  \jessiet{Can use a careful check}
  \btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
  %\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
  As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
  We claim their projections $\{\pi(z_i)\}$ are affinely independent.
  Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
  We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.

@@

%\begin{itemize}
%\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
%\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
%  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
%\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
%\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
%\end{itemize}

Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g$ for any $v \in \V$.

@@

%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
  For $\V' \subseteq \V$, we have
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
  Would like to show
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
  Take any $x\in\reals^\Y_+$.
  %\raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}
  %\raf{Another approach: assume $v^* \in \V^* \setminus \V'$.  Take $z = (x,g(x)) \in \relint(F_{v^*})$.  Argue that $x \not\in \cup_{v\in\V'} \pi(F_v)$.}

@@

\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
  For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
  \btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
  Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
  Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
\end{proof}

Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$
\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
  For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
  \btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
  $\implies$
  The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
  Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

@@

\begin{claim}\label{claim:faces-contained-in-facets}
  If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a nonempty face of $G$, and thus a subset of a facet. 
\end{claim}
\begin{proof}
  Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ and $F_v$ is not empty.
  Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.

  % subset of facet
  Moreover, the faces of $G$ are all convex polyhedra.
  Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
  \btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
\end{proof}

\begin{claim}\label{claim:vface-subset-some-vstar-face}
  For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{proof}
	\jessiet{Can use a careful read}
  $\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $G$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
  Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
  Since $\H = \cap (\H_{\V^*} \cup \H_\Y)$, we are done if $F_v$ is contained in a face of $\H_{\V^*}$ and need to consider the case where $F_v \in \H_\Y$.
